### 2010-03-23 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: Give Nat in type-former-desc.

Consequently, the examples previously developed can be
straightforwardly translated into this new presentation. \note{We
  might want to re-do the Nat example here, as we encode once again in
  $\IDesc$} In the following, we adopt this last version as our de
facto universe of inductive types. In particular, we are going to
evolve this presentation into an indexed one.

>>>>

Consequently, the examples previously developed can be
straightforwardly translated into this new presentation. For example,
here is the new definition of $\NatD$:

\[\stk{
\NatD : \Desc \\
\NatD \mapsto \DSigma{(\EnumT{[ \NatZero, \NatSuc{} ]})}
                     {[ \DUnit \quad \DId ]}
}\]

In the following, we adopt this last version as our de
facto universe of inductive types. In particular, we are going to
evolve this presentation into an indexed one.
